---
title: "Cars Data Presentation"
author: "Vitaliy Pavlenko"
date: "1/7/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Dataset 

### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

```{r, message=FALSE}
library(datasets)
head(mtcars, 3)
```

## Dataset format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2] | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |
---

## Analysis, Server function
```r
shinyServer(function(input, output) {
  output$mpgPlot <- renderPlot({
    # generate plot from input from ui.R
    data = subset(mtcars, cyl==input$cyl)
    plot(mpg ~ disp, data = data)
  })
})
```
