---
title: "Presidential Approval App"
author: "Vitaliy Pavlenko"
date: "1/7/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Dataset 

### Source:
> The (approximately) quarterly approval rating for the President of the United States from the first quarter of 1945 to the last quarter of 1974.

### Preview:
```{r, message=FALSE, echo=TRUE}
library(datasets)
window(presidents, start=c(1956,1), end=c(1960,1))
```

## Data Transforms

Convert Time-series to Data-Frame

```{r, eval=FALSE, echo=TRUE}
pdata = pdata = data.frame(r=as.matrix(presidents), t=time(presidents))
```

Filter for a particular year, specified by input
```{r, eval=FALSE, echo=TRUE}
ydata = pdata[which(pdata$t>=(input$year) & pdata$t<(input$year+1)),]
```


## Server-side plotting

Following script was used for generating plots

```{r, eval=FALSE, echo=TRUE}
    x = c(1,2,3,4)
    plot(x, ydata$r, xlab="Quater", ylab="Rating", 
         main=paste("Year", input$year, sep=" "),
         xlim=c(1,4), ylim=c(0,100), xaxt="n", col="blue")
    axis(1, at = seq(1, 4, by = 1), las=2)
    abline(lm(ydata$r ~ x), col="blue")
    points(x, c(input$q1,input$q2,input$q3,input$q4), pch=20, col="red")
    legend(1, 95, legend=c("Dataset", "Current Input"),
           col=c("blue", "red"), lty=1:1, cex=0.8)
```

## Interesting Findings

It seems that from the dataset, only president Nixon (1974) had lower approval ratings than Trump (2017)
```{r, message=FALSE}
    pdata = pdata = data.frame(r=as.matrix(presidents), t=time(presidents))
    ydata = pdata[which(pdata$t>=(1974) & pdata$t<(1974+1)),]
    
    x = c(1,2,3,4)
    plot(x, ydata$r, xlab="Quater", ylab="Rating", 
         main=paste("Year", 1974, sep=" "),
         xlim=c(1,4), ylim=c(0,100), xaxt="n", col="blue")
    axis(1, at = seq(1, 4, by = 1), las=2)
    abline(lm(ydata$r ~ x), col="blue")
    points(x, c(41.3,38.8,36.9,32.0), pch=20, col="red")
    legend(1, 95, legend=c("Dataset", "Current Input"),
           col=c("blue", "red"), lty=1:1, cex=0.8)
```